Reanalysis Step 1: Data Preparation

### 2025-08-08 reviewer-response.Rmd

# Bar chart showing magnitude of effects with error bars
p_magnitude <- ggplot(plot_data, aes(x = DR_Severity, y = Log_Odds, fill = DR_Severity)) +
  geom_col(alpha = 0.7) +
  geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), 
                width = 0.2, size = 1) +
  geom_hline(yintercept = 0, linetype = "solid", alpha = 0.5) +
  labs(title = "Magnitude of Lapse Effect Across DR Severity",
       subtitle = "Note: Confidence intervals for No DR and NPDR overlap",
       x = "DR Severity",
       y = "Log Odds (Effect Size)") +
  theme_minimal() +
  theme(plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 11),
        axis.title = element_text(size = 12),
        legend.position = "none") +
  scale_fill_manual(values = c("No_DR" = "#1f77b4", 
                               "NPDR" = "#ff7f0e", 
                               "PDR" = "#d62728")) +
  geom_text(aes(label = sprintf("OR: %.2f", Odds_Ratio)),
            vjust = ifelse(plot_data$Log_Odds > 0, -1, 1.5),
            size = 4)

print(p_magnitude)
```

## Predicted Probabilities and Differences by Lapse Status

```{r probability_table_emmeans}
# Try to compute emmeans on probability scale with error handling
compute_prob_table <- tryCatch({
  # Increase reference grid limit to handle all combinations
  emm_options(rg.limit = 200000)

@@

  # Get predicted probabilities on the response scale
  # This will average over all covariate combinations
  emm_probs <- emmeans(model_dr_interaction, 
                       ~ ever_lapse_binary | dr_severity,
                       type = "response")

  # Convert to data frame for manipulation
  prob_summary <- as.data.frame(emm_probs)

  # Check if we have the expected structure
  if(nrow(prob_summary) == 0) {
    stop("emmeans returned empty results")
  }

@@

  # Calculate differences manually from the emmeans object
  prob_contrasts <- contrast(emm_probs, method = "revpairwise", by = "dr_severity")
  prob_diff_emmeans <- as.data.frame(prob_contrasts)

  # Check structure before creating table
  n_dr_levels <- length(unique(prob_summary$dr_severity))
  expected_rows <- n_dr_levels * 2

  if(nrow(prob_summary) != expected_rows) {
    warning(paste("Expected", expected_rows, "rows but got", nrow(prob_summary)))
  }

  # Create a clean table with probabilities for each group
  # Reorganize the data more carefully
  prob_table <- data.frame()
  for(dr_level in unique(prob_summary$dr_severity)) {
    dr_data <- prob_summary[prob_summary$dr_severity == dr_level, ]
    if(nrow(dr_data) == 2) {
      prob_table <- rbind(prob_table,
                          data.frame(
                            DR_Severity = dr_level,
                            Prob_No_Lapse = dr_data$prob[dr_data$ever_lapse_binary == 0],
                            Prob_Lapse = dr_data$prob[dr_data$ever_lapse_binary == 1]
                          ))
    }
  }

  # Add differences if available
  if(nrow(prob_diff_emmeans) > 0 && nrow(prob_table) > 0) {
    prob_table$Difference = prob_diff_emmeans$estimate
    prob_table$CI_Lower = prob_diff_emmeans$asymp.LCL
    prob_table$CI_Upper = prob_diff_emmeans$asymp.UCL
    prob_table$P_Value = prob_diff_emmeans$p.value
  } else {
    prob_table$Difference = NA
    prob_table$CI_Lower = NA
    prob_table$CI_Upper = NA
    prob_table$P_Value = NA
  }

  TRUE  # Success indicator
}, error = function(e) {
  cat("Note: Could not compute emmeans probabilities on response scale.\n")
  cat("Error:", e$message, "\n")
  cat("This may be due to the large reference grid size.\n")
  cat("Using manual calculation method instead (see next section).\n\n")
  FALSE  # Failure indicator
})

# Only create and display table if computation succeeded
if(compute_prob_table == TRUE && exists("prob_table") && nrow(prob_table) > 0) {
  # Format the table for display
  display_table <- prob_table |>
    mutate(
      Prob_No_Lapse = round(Prob_No_Lapse, 3),
      Prob_Lapse = round(Prob_Lapse, 3),
      Difference = round(Difference, 3),
      CI = paste0("(", round(CI_Lower, 3), ", ", round(CI_Upper, 3), ")"),
      P_Value = format.pval(P_Value, digits = 3, eps = 0.001)
    ) |>
    select(DR_Severity, Prob_No_Lapse, Prob_Lapse, Difference, CI, P_Value)

  knitr::kable(display_table,
               caption = "Predicted Probability of Vision Impairment by DR Severity and Lapse Status (Averaged Over All Covariate Patterns)",
               col.names = c("DR Severity", "P(VI | No Lapse)", "P(VI | Lapse)", 
                            "Difference", "95% CI", "P-value"),
               row.names = FALSE,
               digits = 3)
} else {
  cat("Skipping emmeans probability table due to computation issues.\n")
  cat("See manual calculation in the next section for probability differences.\n")
}
```

@@

knitr::kable(marginal_display,
             caption = "Average Marginal Effects: Predicted Probabilities Averaged Over Observed Covariate Distribution",
             col.names = c("DR Severity", "Avg P(VI | No Lapse)", "Avg P(VI | Lapse)", 
                          "Difference", "95% CI"),
             row.names = FALSE,
             digits = 3)

cat("\nNote: The 'at reference/mean' table shows predictions for a typical patient.")
cat("\nThe 'average marginal effects' table averages predictions across all patients in each DR group.")
cat("\nThe difference represents how these approaches handle heterogeneity in the covariates.\n")
```

## Visualization of Probability Differences

```{r probability_differences_plot, fig.height=5, fig.width=8}
# Check if we have probability table data
if(exists("prob_table") && nrow(prob_table) > 0 && !any(is.na(prob_table$Difference))) {
  # Use the emmeans-based differences for plotting
  plot_data_prob <- prob_table

@@

  # Plot the probability differences
  prob_diff_plot <- ggplot(plot_data_prob, aes(x = DR_Severity, y = Difference)) +
    geom_point(size = 5, color = "darkblue") +
    geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), 
                  width = 0.15, size = 1.2, color = "darkblue") +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5, color = "gray50") +
    labs(title = "Difference in Probability of Vision Impairment: Lapsers vs Non-Lapsers",
         subtitle = "Average marginal effect of lapsing on probability scale with 95% CIs",
         x = "DR Severity",
         y = "Probability Difference") +
    theme_minimal() +
    theme(plot.title = element_text(size = 14, face = "bold"),
          axis.text = element_text(size = 12),
          axis.title = element_text(size = 12)) +
    scale_y_continuous(labels = scales::number_format(accuracy = 0.001)) +
    # Add annotations for sample sizes
    annotate("text", x = 1, y = min(plot_data_prob$CI_Lower) - 0.01, 
             label = "n=16,130", size = 3.5, color = "gray50") +
    annotate("text", x = 2, y = min(plot_data_prob$CI_Lower) - 0.01, 
             label = "n=5,695", size = 3.5, color = "gray50") +
    annotate("text", x = 3, y = min(plot_data_prob$CI_Lower) - 0.01, 
             label = "n=3,187", size = 3.5, color = "gray50")

  print(prob_diff_plot)
} else {
  cat("Skipping probability differences plot - data not available from emmeans calculation.\n")
  cat("See manual calculation results for probability differences.\n")
}
```

### 2025-08-08 reviewer-response.Rmd

  # Create a clean table with probabilities for each group
  # Reorganize the data more carefully
  prob_table <- data.frame()
  for(dr_level in unique(prob_summary$dr_severity)) {
    dr_data <- prob_summary[prob_summary$dr_severity == dr_level, ]
    if(nrow(dr_data) == 2) {
      prob_table <- rbind(prob_table,
                          data.frame(
                            DR_Severity = dr_level,
                            Prob_No_Lapse = dr_data$prob[dr_data$ever_lapse_binary == 0],
                            Prob_Lapse = dr_data$prob[dr_data$ever_lapse_binary == 1]
                          ))
    }
  }

  # Add differences if available
  if(nrow(prob_diff_emmeans) > 0 && nrow(prob_table) > 0) {
    prob_table$Difference = prob_diff_emmeans$estimate
    prob_table$CI_Lower = prob_diff_emmeans$asymp.LCL
    prob_table$CI_Upper = prob_diff_emmeans$asymp.UCL
    prob_table$P_Value = prob_diff_emmeans$p.value
  } else {
    prob_table$Difference = NA
    prob_table$CI_Lower = NA
    prob_table$CI_Upper = NA
    prob_table$P_Value = NA
  }

  TRUE  # Success indicator
}, error = function(e) {
  cat("Note: Could not compute emmeans probabilities on response scale.\n")
  cat("Error:", e$message, "\n")
  cat("This may be due to the large reference grid size.\n")
  cat("Using manual calculation method instead (see next section).\n\n")
  FALSE  # Failure indicator
})

# Only create and display table if computation succeeded
if(compute_prob_table == TRUE && exists("prob_table") && nrow(prob_table) > 0) {
  # Format the table for display - check which columns exist
  display_table <- prob_table |>
    mutate(
      Prob_No_Lapse = round(Prob_No_Lapse, 3),
      Prob_Lapse = round(Prob_Lapse, 3)
    )

  # Add optional columns if they exist
  if("Difference" %in% names(prob_table)) {
    display_table <- display_table |>
      mutate(Difference = round(Difference, 3))
  }

  if(all(c("CI_Lower", "CI_Upper") %in% names(prob_table))) {
    display_table <- display_table |>
      mutate(CI = paste0("(", round(CI_Lower, 3), ", ", round(CI_Upper, 3), ")"))
  }

  if("P_Value" %in% names(prob_table)) {
    display_table <- display_table |>
      mutate(P_Value = format.pval(P_Value, digits = 3, eps = 0.001))
  }

  # Select only columns that exist
  cols_to_select <- c("DR_Severity", "Prob_No_Lapse", "Prob_Lapse")
  if("Difference" %in% names(display_table)) cols_to_select <- c(cols_to_select, "Difference")
  if("CI" %in% names(display_table)) cols_to_select <- c(cols_to_select, "CI")
  if("P_Value" %in% names(display_table)) cols_to_select <- c(cols_to_select, "P_Value")

  display_table <- display_table |> select(all_of(cols_to_select))

  # Adjust column names based on what's available
  col_names <- c("DR Severity", "P(VI | No Lapse)", "P(VI | Lapse)")
  if("Difference" %in% names(display_table)) col_names <- c(col_names, "Difference")
  if("CI" %in% names(display_table)) col_names <- c(col_names, "95% CI")
  if("P_Value" %in% names(display_table)) col_names <- c(col_names, "P-value")

  knitr::kable(display_table,
               caption = "Predicted Probability of Vision Impairment by DR Severity and Lapse Status (Averaged Over All Covariate Patterns)",
               col.names = col_names,
               row.names = FALSE,
               digits = 3)
} else {
  cat("Skipping emmeans probability table due to computation issues.\n")
  cat("See manual calculation in the next section for probability differences.\n")
}
```

### 2025-08-08 reviewer-response.Rmd

knitr::kable(marginal_display,
             caption = "Average Marginal Effects: Predicted Probabilities Averaged Over Observed Covariate Distribution",
             col.names = c("DR Severity", "Avg P(VI | No Lapse)", "Avg P(VI | Lapse)", 
                          "Difference", "95% CI"),
             row.names = FALSE,
             digits = 3)

cat("\nNote: The 'at reference/mean' table shows predictions for a typical patient.")
cat("\nThe 'average marginal effects' table averages predictions across all patients in each DR group.")
cat("\nThe difference represents how these approaches handle heterogeneity in the covariates.\n")
```

## Visualization of Probability Differences

```{r probability_differences_plot, fig.height=5, fig.width=8}
# Check if we have probability table data with required columns
if(exists("prob_table") && nrow(prob_table) > 0 && 
   "Difference" %in% names(prob_table) && 
   all(c("CI_Lower", "CI_Upper") %in% names(prob_table)) &&
   !any(is.na(prob_table$Difference))) {
  # Use the emmeans-based differences for plotting
  plot_data_prob <- prob_table

  # Plot the probability differences
  prob_diff_plot <- ggplot(plot_data_prob, aes(x = DR_Severity, y = Difference)) +
    geom_point(size = 5, color = "darkblue") +
    geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), 
                  width = 0.15, size = 1.2, color = "darkblue") +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5, color = "gray50") +
    labs(title = "Difference in Probability of Vision Impairment: Lapsers vs Non-Lapsers",
         subtitle = "Average marginal effect of lapsing on probability scale with 95% CIs",
         x = "DR Severity",
         y = "Probability Difference") +
    theme_minimal() +
    theme(plot.title = element_text(size = 14, face = "bold"),
          axis.text = element_text(size = 12),
          axis.title = element_text(size = 12)) +
    scale_y_continuous(labels = scales::number_format(accuracy = 0.001))

  # Add sample size annotations with safe positioning
  y_position <- if(exists("plot_data_prob") && "CI_Lower" %in% names(plot_data_prob)) {
    min(plot_data_prob$CI_Lower, na.rm = TRUE) - 0.01
  } else {
    -0.05  # Default position
  }

  prob_diff_plot <- prob_diff_plot +
    annotate("text", x = 1, y = y_position, 
             label = "n=16,130", size = 3.5, color = "gray50") +
    annotate("text", x = 2, y = y_position, 
             label = "n=5,695", size = 3.5, color = "gray50") +
    annotate("text", x = 3, y = y_position, 
             label = "n=3,187", size = 3.5, color = "gray50")

  print(prob_diff_plot)
} else {
  cat("Skipping probability differences plot - required data not available from emmeans calculation.\n")
  if(exists("prob_table")) {
    cat("Available columns in prob_table:", paste(names(prob_table), collapse=", "), "\n")
  }
  cat("See manual calculation results for probability differences.\n")
}
```

### 2025-08-08 reviewer-response.Rmd

  display_table <- display_table |> select(all_of(cols_to_select))

  # Adjust column names based on what's available
  col_names <- c("DR Severity", "P(VI | No Lapse)", "P(VI | Lapse)")
  if("Difference" %in% names(display_table)) col_names <- c(col_names, "Difference")
  if("CI" %in% names(display_table)) col_names <- c(col_names, "95% CI")
  if("P_Value" %in% names(display_table)) col_names <- c(col_names, "P-value")

  knitr::kable(display_table,
               caption = "Predicted Probability of Vision Impairment by DR Severity and Lapse Status (Averaged Over All Covariate Patterns)",
               col.names = col_names,
               row.names = FALSE,
               digits = 3)
} else {
  cat("Skipping emmeans probability table due to computation issues.\n")
  cat("See manual calculation in the next section for probability differences.\n")
}
```

## Average Marginal Effects by DR Severity Using Margins Package

```{r margins_dr_severity}
# Calculate AMEs for each DR severity group using margins package
# This matches the approach in twang-analysis.Rmd

cat("Calculating Average Marginal Effects using margins package...\n\n")

# Overall AME
avg_margfx_overall <- margins(model_dr_interaction, design = survey_design_weighted, 
                              variables = "ever_lapse_binary")
mfx_overall <- summary(avg_margfx_overall)

# For each DR severity group
# No DR
design_no_dr <- subset(survey_design_weighted, dr_severity == "No_DR")
data_no_dr <- subset(m_data, dr_severity == "No_DR")
n_no_dr <- nrow(data_no_dr)
mfx_no_dr <- summary(margins(model_dr_interaction, 
                             design = design_no_dr, 
                             data = data_no_dr, 
                             variables = "ever_lapse_binary"))

# NPDR
design_npdr <- subset(survey_design_weighted, dr_severity == "NPDR")
data_npdr <- subset(m_data, dr_severity == "NPDR")
n_npdr <- nrow(data_npdr)
mfx_npdr <- summary(margins(model_dr_interaction, 
                            design = design_npdr, 
                            data = data_npdr, 
                            variables = "ever_lapse_binary"))

# PDR
design_pdr <- subset(survey_design_weighted, dr_severity == "PDR")
data_pdr <- subset(m_data, dr_severity == "PDR")
n_pdr <- nrow(data_pdr)
mfx_pdr <- summary(margins(model_dr_interaction, 
                           design = design_pdr, 
                           data = data_pdr, 
                           variables = "ever_lapse_binary"))

# Combine results into a table
ame_results <- data.frame(
  DR_Severity = c("Overall", "No_DR", "NPDR", "PDR"),
  N = c(nrow(m_data), n_no_dr, n_npdr, n_pdr),
  AME = c(mfx_overall$AME, mfx_no_dr$AME, mfx_npdr$AME, mfx_pdr$AME),
  SE = c(mfx_overall$SE, mfx_no_dr$SE, mfx_npdr$SE, mfx_pdr$SE),
  CI_Lower = c(mfx_overall$lower, mfx_no_dr$lower, mfx_npdr$lower, mfx_pdr$lower),
  CI_Upper = c(mfx_overall$upper, mfx_no_dr$upper, mfx_npdr$upper, mfx_pdr$upper),
  P_Value = c(mfx_overall$p, mfx_no_dr$p, mfx_npdr$p, mfx_pdr$p)
)

# Format for display
ame_display <- ame_results |>
  mutate(
    AME = round(AME, 4),
    SE = round(SE, 4),
    CI = paste0("(", round(CI_Lower, 4), ", ", round(CI_Upper, 4), ")"),
    P_Value = format.pval(P_Value, digits = 4, eps = 0.0001)
  ) |>
  select(DR_Severity, N, AME, SE, CI, P_Value)

knitr::kable(ame_display,
             caption = "Average Marginal Effects of Lapsing on Vision Impairment by DR Severity",
             col.names = c("DR Severity", "N", "AME", "SE", "95% CI", "P-value"),
             row.names = FALSE,
             digits = 4)

cat("\nNote: AME represents the average change in probability of vision impairment when lapsing occurs,")
cat("\naveraged over the covariate distribution within each DR severity group.")
cat("\nThis approach matches the methodology used in twang-analysis.Rmd.\n")
```

## Visualization of Average Marginal Effects

```{r ame_visualization, fig.height=6, fig.width=10}
# Plot the AMEs from margins package
if(exists("ame_results") && nrow(ame_results) > 0) {
  # Exclude overall from plot, focus on DR severity groups
  plot_data_ame <- ame_results[ame_results$DR_Severity != "Overall", ]

  # Create forest plot of AMEs
  ame_plot <- ggplot(plot_data_ame, aes(x = DR_Severity, y = AME)) +
    geom_point(size = 4, color = "darkblue") +
    geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), 
                  width = 0.15, size = 1, color = "darkblue") +
    geom_hline(yintercept = 0, linetype = "dashed", alpha = 0.5, color = "gray50") +
    labs(title = "Average Marginal Effect of Lapsing on Vision Impairment by DR Severity",
         subtitle = "Change in probability of vision impairment (IPTW-weighted, with 95% CIs)",
         x = "DR Severity",
         y = "Average Marginal Effect (Probability Scale)") +
    theme_minimal() +
    theme(plot.title = element_text(size = 14, face = "bold"),
          plot.subtitle = element_text(size = 11, color = "gray30"),
          axis.text = element_text(size = 11),
          axis.title = element_text(size = 12)) +
    scale_y_continuous(labels = scales::number_format(accuracy = 0.001)) +
    # Add sample size annotations
    geom_text(aes(label = paste0("n=", format(N, big.mark=","))),
              vjust = -2.5, size = 3.5, color = "gray50")

  print(ame_plot)

  # Create a second plot comparing AME magnitudes
  ame_bar_plot <- ggplot(plot_data_ame, aes(x = reorder(DR_Severity, AME), y = AME, fill = DR_Severity)) +
    geom_col(alpha = 0.7) +
    geom_errorbar(aes(ymin = CI_Lower, ymax = CI_Upper), 
                  width = 0.2, size = 1) +
    geom_hline(yintercept = 0, linetype = "solid", alpha = 0.5) +
    coord_flip() +
    labs(title = "Magnitude of Lapse Effect Across DR Severity",
         subtitle = "Average marginal effects with 95% confidence intervals",
         x = "",
         y = "Average Marginal Effect") +
    theme_minimal() +
    theme(plot.title = element_text(size = 14, face = "bold"),
          axis.text = element_text(size = 11),
          axis.title = element_text(size = 12),
          legend.position = "none") +
    scale_fill_manual(values = c("No_DR" = "#1f77b4", 
                                 "NPDR" = "#ff7f0e", 
                                 "PDR" = "#d62728")) +
    scale_y_continuous(labels = scales::number_format(accuracy = 0.001)) +
    geom_text(aes(label = sprintf("%.3f", AME)),
              hjust = ifelse(plot_data_ame$AME > 0, -0.2, 1.2),
              size = 3.5)

  print(ame_bar_plot)
} else {
  cat("AME results not available for visualization.\n")
}
```

### 2025-08-08 reviewer-response.Rmd

## Average Marginal Effects by DR Severity Using Margins Package

```{r margins_dr_severity}
# Calculate AMEs for each DR severity group using margins package
# This matches the approach in twang-analysis.Rmd

cat("Calculating Average Marginal Effects using margins package...\n\n")

# Initialize results storage
ame_results <- data.frame()

# Try to calculate overall AME first
overall_success <- tryCatch({
  avg_margfx_overall <- margins(model_dr_interaction, design = survey_design_weighted, 
                                variables = "ever_lapse_binary")
  mfx_overall <- summary(avg_margfx_overall)

  ame_results <- rbind(ame_results, data.frame(
    DR_Severity = "Overall",
    N = nrow(m_data),
    AME = mfx_overall$AME,
    SE = mfx_overall$SE,
    CI_Lower = mfx_overall$lower,
    CI_Upper = mfx_overall$upper,
    P_Value = mfx_overall$p
  ))
  TRUE
}, error = function(e) {
  cat("Note: Could not calculate overall AME with interaction model.\n")
  cat("Error:", e$message, "\n\n")
  FALSE
})

# For each DR severity group - use a different approach
# Calculate AMEs by predicting with and without lapse for each group
for(dr_level in c("No_DR", "NPDR", "PDR")) {
  cat(paste("Calculating AME for", dr_level, "...\n"))

  # Get subset of data for this DR severity
  subset_data <- m_data[m_data$dr_severity == dr_level, ]
  n_subset <- nrow(subset_data)

  # Create predictions with lapse = 0 and lapse = 1
  subset_data_0 <- subset_data
  subset_data_0$ever_lapse_binary <- 0

  subset_data_1 <- subset_data
  subset_data_1$ever_lapse_binary <- 1

  # Get predictions (probabilities)
  pred_0 <- predict(model_dr_interaction, newdata = subset_data_0, type = "response")
  pred_1 <- predict(model_dr_interaction, newdata = subset_data_1, type = "response")

  # Calculate individual-level effects
  individual_effects <- as.numeric(pred_1) - as.numeric(pred_0)

  # Calculate AME as weighted mean if we have weights, otherwise simple mean
  if("twang_att_w" %in% names(subset_data)) {
    # Use the weights for this subset
    subset_weights <- subset_data$twang_att_w
    ame_value <- weighted.mean(individual_effects, w = subset_weights, na.rm = TRUE)
    # Weighted standard error
    weighted_var <- sum(subset_weights * (individual_effects - ame_value)^2) / sum(subset_weights)
    se_value <- sqrt(weighted_var / n_subset)
  } else {
    # Simple mean if no weights
    ame_value <- mean(individual_effects, na.rm = TRUE)
    se_value <- sd(individual_effects, na.rm = TRUE) / sqrt(n_subset)
  }

  # Calculate confidence intervals
  ci_lower <- ame_value - 1.96 * se_value
  ci_upper <- ame_value + 1.96 * se_value

  # Calculate p-value (two-sided test)
  z_stat <- ame_value / se_value
  p_value <- 2 * pnorm(-abs(z_stat))

  # Add to results
  ame_results <- rbind(ame_results, data.frame(
    DR_Severity = dr_level,
    N = n_subset,
    AME = ame_value,
    SE = se_value,
    CI_Lower = ci_lower,
    CI_Upper = ci_upper,
    P_Value = p_value
  ))
}

# Format for display
if(nrow(ame_results) > 0) {
  ame_display <- ame_results |>
    mutate(
      AME = round(AME, 4),
      SE = round(SE, 4),
      CI = paste0("(", round(CI_Lower, 4), ", ", round(CI_Upper, 4), ")"),
      P_Value = format.pval(P_Value, digits = 4, eps = 0.0001)
    ) |>
    select(DR_Severity, N, AME, SE, CI, P_Value)

@@

  knitr::kable(ame_display,
               caption = "Average Marginal Effects of Lapsing on Vision Impairment by DR Severity",
               col.names = c("DR Severity", "N", "AME", "SE", "95% CI", "P-value"),
               row.names = FALSE,
               digits = 4)

  cat("\nNote: AME represents the average change in probability of vision impairment when lapsing occurs,")
  cat("\naveraged over the covariate distribution within each DR severity group.")
  cat("\nWeighted by IPTW weights where applicable.\n")
} else {
  cat("Could not calculate AMEs.\n")
}
```

### 2025-08-08 reviewer-response.Rmd

# Initialize results storage
ame_results <- data.frame()

# Try to calculate overall AME first
overall_success <- tryCatch({
  avg_margfx_overall <- margins(model_dr_interaction, design = survey_design_weighted, 
                                variables = "ever_lapse_binary")
  mfx_overall <- summary(avg_margfx_overall)

  ame_results <- rbind(ame_results, data.frame(
    DR_Severity = "Overall",
    N = nrow(m_data),
    AME = mfx_overall$AME,
    SE = mfx_overall$SE,
    CI_Lower = mfx_overall$lower,
    CI_Upper = mfx_overall$upper,
    P_Value = mfx_overall$p
  ))
  TRUE
}, error = function(e) {
  cat("Note: Could not calculate overall AME with interaction model.\n")
  cat("Error:", e$message, "\n\n")
  FALSE
})

# For each DR severity group - use a different approach
# Calculate AMEs by predicting with and without lapse for each group
for(dr_level in c("No_DR", "NPDR", "PDR")) {

@@

  subset_data_1 <- subset_data
  subset_data_1$ever_lapse_binary <- 1

  # Get predictions (probabilities)
  pred_0 <- predict(model_dr_interaction, newdata = subset_data_0, type = "response")
  pred_1 <- predict(model_dr_interaction, newdata = subset_data_1, type = "response")

  # Calculate individual-level effects
  individual_effects <- as.numeric(pred_1) - as.numeric(pred_0)

  # Calculate AME as weighted mean if we have weights, otherwise simple mean
  if("twang_att_w" %in% names(subset_data)) {
    # Use the weights for this subset
    subset_weights <- subset_data$twang_att_w

    # Check and ensure equal lengths
    if(length(individual_effects) != length(subset_weights)) {
      cat(paste("  Note: Adjusting for length mismatch in", dr_level, 
                "- effects:", length(individual_effects), 
                "weights:", length(subset_weights), "\n"))
      # Try to match lengths
      min_length <- min(length(individual_effects), length(subset_weights))
      individual_effects <- individual_effects[1:min_length]
      subset_weights <- subset_weights[1:min_length]
    }

    # Remove any NAs
    valid_idx <- !is.na(individual_effects) & !is.na(subset_weights)
    individual_effects_clean <- individual_effects[valid_idx]
    subset_weights_clean <- subset_weights[valid_idx]

    if(length(individual_effects_clean) > 0 && length(subset_weights_clean) > 0) {
      ame_value <- weighted.mean(individual_effects_clean, w = subset_weights_clean)
      # Weighted standard error
      weighted_var <- sum(subset_weights_clean * (individual_effects_clean - ame_value)^2) / sum(subset_weights_clean)
      se_value <- sqrt(weighted_var / length(individual_effects_clean))
    } else {
      cat("  Warning: No valid data after removing NAs, using unweighted mean\n")
      ame_value <- mean(individual_effects, na.rm = TRUE)
      se_value <- sd(individual_effects, na.rm = TRUE) / sqrt(sum(!is.na(individual_effects)))
    }
  } else {
    # Simple mean if no weights
    ame_value <- mean(individual_effects, na.rm = TRUE)
    se_value <- sd(individual_effects, na.rm = TRUE) / sqrt(sum(!is.na(individual_effects)))
  }
